---
title: "Assignment3"
author: "Suad Al Darra - 17234582"
date: "19 Oct 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Binomial Distribution
Q1
At a certain airport, 75% of the flights arrive on time. A sample of 10 flights is studied.

###i. Find the probability that all 10 of the flights were on time.
```{r}
dbinom(10,10,0.75)
```
0.0563 which is not very likely to happen

###ii. Find the probability that 7 to 9 flights were on time
```{r}

sum(dbinom(7:9,10,0.75))
```
0.7195616 

Q2. A large industrial firm allows a discount on any invoice that is paid within 30 days. Of all
invoices, 10% receive the discount. In a company audit, 50 invoices are sampled at random.


###i. What is the probability that fewer than 10 of the 50 sampled invoices receive the discount?
```{r}
n <- 50
x <-10
p <-0.10
sum(dbinom(0:x-1,n,p)) #or sum(pbinom(x-1,n,p,lower.tail = TRUE))

```
Less than 10 P(X=0,1,2..9) = 0.9754621 

###ii. Calculate the mean to determine the most likely number of discounts that company will have to offer.
```{r}
#mean = n * p 
n * p
```
the most likely number of discounts is 5

###iii. Chebyshev's inequality states that at least 75% of the observations will be in the range of the mean ±2 times the standard deviation. Calculate the standard deviation and use Chebyshev's inequality to provide a range of values that likely account for 75% of discounts the firm expect to give.

```{r}
sd <- sqrt((n*p*(1-p)))
sd
```
Standard deviation is 2.121. Range of values most likely to be in in the 75% discounts are [5-2.121,5+2.121] = [2.879, 7.121]
Rounding, most likely number of discounts will be between 3 and 7.



## Poisson Distribution.

Q3. The number of cars arriving at a given roundabout follows a Poisson distribution with a
mean rate of 3 per second.

###i. What is the probability that 3 cars arrive in a given second?
```{r}
dpois(3,3)
```

###ii. What is the probability that more than 3 cars arrive in a given second?

```{r}
ppois(3,3,lower=FALSE)
```

Q4. The number of hits on a certain website follows a Poisson distribution with a mean rate
of 4 per minute.

###i. What is the probability that 5 messages are received in a given minute?
```{r}
dpois(x = 5,lambda = 4)
```

###ii. What is the probability that 9 messages are received in 1.5 minutes?
```{r}
dpois(x = 9,lambda = 4*1.5)
```

###iii. What is the probability that fewer than 3 messages are received in a period of 30 seconds?
```{r}

sum(dpois(x = 0:3,lambda = 4/2))
```

