---
title: "Binomial Distribution examples"
author: "John Newell"
date: "25 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Calculating probabilities using the binomial distribution

## Camera test example.

 n=3, p=0.8
 What is the prob that two cameras pass in 3 tests ?
 
This can be answered by assuming that the random variable of interest (i.e. the number of passes) follows a binomial distribution with probability 0.8 and number of trials equal to 3.  The command bnneded is '# dbinom(x, size, prob)' and the required probability is:
 
 
```{r}
dbinom(x=2, size=3, prob=0.8)
```

i.e. the probability of two passing in 3 tests is 0.34.


## Pollutant example

Let X denote the number of samples that contain the pollutant in the next 18 samples analyzed. Then X is a binomial random variable with p = 0.1 and n = 18. The question askes you to find the probability that, in the next 18 samples exactly 2 contain the pollutant.

the required probability is:
```{r}

```
 
 
```{r}
dbinom(x=2, size=18, prob=0.1)
```

i.e. the probability that in the next 18 samples exactly 2 contain the pollutant is 0.28.

The second part of the question asks you to determine the probability that
there are between 3 and 6 samples contain pollutants i.e. 3 <= X < 7. You can do this several ways.

Long way:

```{r}
  dbinom(x=3, size=18, prob=0.1) + dbinom(x=4, size=18, prob=0.1) +
  dbinom(x=5, size=18, prob=0.1) + dbinom(x=6, size=18, prob=0.1)
```

or more cleverly using the sum function in R as follows:

```{r}
sum(dbinom(3:6, size = 18, prob=0.1))
```


Both give the same answer, a probability of 0.265.  How would you interpret this probability ?


