---
title: "Poisson Distribution examples"
author: "John Newell"
date: "25 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Calculating probabilities using the Poisson distribution

## Flaws on Copper Wire example.

Suppose that the number of flaws on a thin copper wire follows a Poisson distribution with a mean of 2.3 flaws per mm. 

Find the probability of exactly 2 flaws in 1 mm of wire
 
 
```{r}
dpois(x=2, lambda=2.3)
```

i.e. the probability of exactly two flaws in 1mm of wire is 0.265.

## Flaws on Copper Wire example revisited.

Suppose that the number of flaws on a thin copper wire follows a Poisson distribution with a mean of 2.3 flaws per mm. Determine the probability of 10 flaws in 5 mm of wire.

The required probability is:
```{r}
dpois(x=10, lambda=2.3*5)
```
 
i.e. the probability that in the next 18 samples exactly 2 contain the pollutant is 0.11.

How would you interpret this probability ?


