---
title: "Training Intervention Analysis"
author: "Suad Al Darra - 17234582"
date: "17 October 2018"
output:
  html_document: default
  word_document: default
---

## Context: Celtic Study introduced in class.

Scaffold for the analysis when the primary response variable is VO2 max.  YOu need to rerun the analysis using the Squat variables (i.e. Squat_Pre, Squat_Post) to see if there has been any improvemnt on average and provide a tolerance interval for teh likely improvement for 95% of players in the populaiton of interest (with 95% confidence).



```{r}
library(infer)
library(tidyverse)
library(tolerance)
```

## Read in the training intervention data

Read in the data and have a look at the variable names and structure of the data.

```{r}

train.df <- read.csv("Training_intervention_data.CSV")
glimpse(train.df)
```

## Focus on the VO2 max response variables.


## Summary Statistics



```{r}
train.df %>% select(VO2.max_Pre,VO2.max_Post) %>% summary()

```

## Mean and Standard Deviation

```{r}

train.df %>% select(VO2.max_Pre,VO2.max_Post) %>%
            summarize(Pre_Mean=mean(VO2.max_Pre), Pre_SD= sd(VO2.max_Pre),
                      Post_Mean=mean(VO2.max_Post), Post_SD= sd(VO2.max_Post))

```

## Scatterplot of Pre and Post with line of equality

```{r}
train.df %>% ggplot(aes(x = VO2.max_Pre, y = VO2.max_Post)) +
        geom_point() + 
  ggtitle("Scatterplot of Pre and Post VO2 Max") +
  ylab("Post VO2 Max (units ?)") +
  xlab("Post VO2 Max (units ?)") +
  geom_abline(slope=1, intercept=0)
  
```


## Calculate the Improvement

Calculate a new variable and have a look at the data frame to see that it has been created.  High vlaues of VO2 max are good to Post-Pre is a better measure than Pre-Post to capture this.

```{r}

train.df <- train.df %>% mutate(Improvement = VO2.max_Post-VO2.max_Pre) %>%
              glimpse()
  


```

## Mean and Standard Deviation of Improvement

```{r}

train.df %>% select(Improvement) %>%
            summarize(Imp_Mean=mean(Improvement), Imp_SD= sd(Improvement))

```


## Boxplot of Improvement

```{r}


train.df %>% ggplot(aes(x = "", y = Improvement)) +
        geom_boxplot() + 
  ggtitle("Boxplot of Improvment in VO2 Max") +
  ylab("Improvment in VO2 Max (units ?)") +
  xlab("") +
  coord_flip()

```

95% Confidence Interval


## Using the t.test function

```{r}

train.df %>% select(Improvement) %>% t.test()

```


95% Bootstrap CI for the mean

```{r}

boot <- train.df %>%
  specify(response = Improvement) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")

percentile_ci <- get_ci(boot)
round(percentile_ci,2)

```

```{r}
boot %>% visualize(endpoints = percentile_ci, direction = "between") +
                   xlab("Bootstrap Mean") + ylab("Frequency")

```



95% Bootstrap CI for the medan

```{r}

boot.median <- train.df %>%
  specify(response = Improvement) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median")

percentile_ci_median <- get_ci(boot.median)
round(percentile_ci_median,2)

```

```{r}
boot.median %>% visualize(endpoints = percentile_ci_median, direction = "between") +
                   xlab("Bootstrap Median") + ylab("Frequency")

```


95% Tolerance Interval

```{r}

normtol.int(train.df$Improvement, alpha = 0.05, P = 0.95)

```


## Conclusion ??